---
title: "repproduce"
author: "CVT"
format: html
---

1. Name: Christian Velling Thorup 
2. Affiliation Department of Cardiology, Aarhus University Hospital, Steno Diabetes Center, Aarhus University Hospital and Department of Biomedicine
3. Aarhus University

# Intro 

**Der var en gang en Christian. Christian var sej**

*S책 sej*

# Methods and Results

**Christian er sej**

*S책 sej*

## Analysis

**Christian er sej**

*S책 sej*

# Discussion

**Christian er sej**

*S책 sej*

```{r}
2+2
```

```{r setup}
#| message: false
#| warning: false
library(tidyverse)
library(NHANES)
NHANES_small <- read_csv(here::here("data/NHANES_small.csv"))
```

```{r}
NHANES_small <- select(NHANES_small, age, sex, bmi, diabetes, phys_active, bp_sys_ave, bp_dia_ave, education)

NHANES_small
```
#Table of results 
```{r}
#| warning: false
NHANES_small %>%
  filter(!is.na(diabetes)) %>%
  group_by(diabetes, education) %>%
  summarise(
    mean_age = mean(age, na.rm = TRUE),
    mean_bmi = mean(bmi, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  knitr::kable(caption = "Mean values of Age and BMI for each education and diabetes status")
```

## Prettier table
```{r}
#| warning: false
#| echo: false
NHANES_small %>%
  filter(!is.na(diabetes), !is.na(education)) %>%
  group_by(diabetes, education) %>%
  summarise(
    mean_age = mean(age, na.rm = TRUE),
    mean_bmi = mean(bmi, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  mutate(
    # Task 2a.
    mean_age = round(mean_age, 1),
    mean_bmi = round(mean_bmi, 1),
    # Task 2b.
    education = str_to_sentence(education)
  ) %>% 
  rename(
    # Task 3.
    "Diabetes Status" = diabetes,
    "Education" = education,
    "Mean Age" = mean_age,
    "Mean BMI" = mean_bmi
  ) %>% 
  knitr::kable(caption = "Mean values of Age and BMI for each education and diabetes status.")
```


